Nail: A practical interface generator for data formats

### 2014-05-01 paper/osdi14/eval.tex
checkpoint eval (partway through 5.1)

In our evaluation of Nail, we try to answer four questions:

@@

\subsection{Data formats}
\label{s:eval-formats}
To answer the first question, we implemented grammars for four protocols with particularly
challenging features and show that Nail is a good fit for these data formats and some aspects of
these formats would be very hard to parse with other parser generators.
Figure~\ref{fig:eval-protocols} lists various example protocols we have implemented.

\begin{figure}[tb]
\label{fig:eval-protocols}
\begin{tabular}{@{}lll@{}}
\toprule
\textbf{Protocol} & \textbf{LoC} & \textbf{Problematic features} \\ 
\midrule
DNS messages &  48+64 & Label compression\\
& & Count fields \\
ZIP archives & 92 + 78 & Checksums, \\ 
& & compression, offsets, \\
& &  variable length trailer\\ 
Ethernet frames & 16 & \\
ARP &  10  & \\
IP &  25 & Total Length field, options \\
UDP & 7 & Checksum, Length field \\
ICMP & 5 & Checksum \\
\bottomrule

\end{tabular}
\caption{Example Nail grammars, their code size of the grammar plus  the transformations they use
  and protocol features that cannot be expressed in existing grammar languages. }
\end{figure}
\subsubsection{DNS.}

>>>>

In our evaluation of Nail, we answer four questions:

@@

\subsection{Data formats}
\label{s:eval-formats}

To answer the first question, we used Nail to implement grammars
for seven protocols with a range of challenging features.
Figure~\ref{fig:eval-protocols} summarizes these protocols, the lines
of code for their Nail grammars, and the challenging features that make
the protocols difficult to parse with state-of-the-art parser generators.
We find that despite the challenging aspects of these protocols, Nail is
able to capture the protocols, by relying on its novel features: dependent
fields, streams, and transforms.  In contrast, state-of-the-art parser
generators would be unable to fully handle 5 out of the 7 data formats.

\begin{figure}[tb]
\centering
\begin{tabular}{lrl}
\toprule
\textbf{Protocol} & \textbf{LoC} & \textbf{Challenging features} \\ 
\midrule
DNS packets & 48+64 & Label compression,\\
  & & count fields \\
ZIP archives & 92+78 & Checksums, offsets, \\ 
  & & variable length trailer, \\
  & & compression \\
Ethernet & 16 & --- \\
ARP & 10 & --- \\
IP & 25 & Total length field, options \\
UDP & 7 & Checksum, length field \\
ICMP & 5 & Checksum \\
\bottomrule
\end{tabular}

\caption{Protocols, sizes of their Nail grammars, and challenging aspects
of the protocol that cannot be expressed in existing grammar languages.
A + symbol counts lines of Nail grammar code (before the +) and lines of
C code for protocol-specific transforms (after the +).}
\label{fig:eval-protocols}
\end{figure}

\subsubsection{DNS.}
